\begin{thebibliography}{99}

\bibitem{Paxson95}
V.~Paxson, S.~Floyd.
Wide area traffic: the failure of poisson modeling.
\textit{IEEE/ACM Transaction on Networking}, 1995.

\bibitem{Royer01}
E.~Royer, P.~Melliar-Smith, L.~Moser.
An Analysis of the Optimum Node Density for Ad hoc Mobile Networks.
\textit{Proceedings of IEEE ICC '01}, 2001.

% TODO: references on Lyapunov's Central Limit Theorem.

%\bibitem{Stevens93}
%W.~Stevens.
%\textit{TCP/IP Illustrated, Volume 1: The Protocols}.
%Addison-Wesley Professional, 1st edition, 1993.

%\bibitem{Tanenbaum96}
%A.~Tanenbaum. \textit{Computer Networks}. Prentice Hall, Upper Saddle River NJ, 3rd edition, 1996.

\bibitem{Clark88}
D.~Clark.
The Design Philosophy of the DARPA Internet Protocols.
\textit{Proceedings of ACM SIGCOMM '88}, 1988.

%\bibitem{Saltzer84} J.~Saltzer, D.~Reed,  D.~Clark. End-to-End Arguments in System Design. \textit{ACM Transactions on Computer Systems}, 1984.

\bibitem{Paxson97}
V.~Paxson, S.~Floyd.
Why we don't know how to simulate the Internet.
\textit{Proceedings of 1997 Winter Simulation Conference}, Atlanta, GA, December 1997.

%\bibitem{Faloutsos99}
%M.~Faloutsos, P.~Faloutsos, C.~Faloutsos.
%On power-law relationships of the Internet topology.
%\textit{Proceedings of ACM SIGCOMM'99}, Cambridge MA,
%  August 1999.

%\bibitem{Medina00}
%A.~Medina, I.~Matta, J.~Byers.
%On the origin of power laws in Internet topologies.
%\textit{ACM Computer Communication Review}, April 2000.

%\bibitem{Zegura97}
%E.~Zegura, K.~Calvert, M.~Donahoo.
%A quantitative comparison of graph-based models for Internet topology.
%\textit{IEEE/ACM Transactions on Networking}, December 1997.

\bibitem{Doar97}
M.~Doar.
A better model for generating test networks.
\textit{Proceedings of IEEE Global Internet (GLOBECOM'97)}, London, UK, November 1997.
  
\bibitem{Satyanarayanan96}
M.~Satyanarayanan.
Fundamental challenges in mobile computing.
\textit{Proceedings of ACM Symposium on Principles of Distributed Computing}, Philadelphia PA, May 1996.

\bibitem{Macker98}
J.~Macker, M.~Corson.
Mobile ad hoc networking and the IETF.
\textit{ACM Mobile Computing and Communications Review}, 1998.

\bibitem{Perrone03}
L.~Perrone, Y.~Yuan, D.~Nicol.
Modeling and Simulation Best Practices for Wireless Ad hoc Networks.
\textit{Proceedings of the Winter Simulation Conference}, December 2003.

%\bibitem{Ash65}
%R.~Ash. \textit{Information Theory}. Interscience Publishers, New York NY, 1965.

%\bibitem{Harvey93}
%A.~Harvey.
%\textit{Time Series Models}.
%The MIT Press, Cambridge MA, 2nd edition, 1993.

%\bibitem{Dubois93}
%D.~Dubois, H.~Prade.
%Fuzzy sets and probability: Misunderstandings, bridges and gaps.
%\textit{Proceedings of Second IEEE International Conference on Fuzzy Systems}, Piscataway NJ, 1993.

%\bibitem{Box94}
%G.~Box, G.~Jenkins.
%\textit{Time Series Analysis: Forecasting \& Control}.
%Holden-Day, 2nd edition, 1994.

%\bibitem{Kokoszka95}
%P.~Kokoszka, M.~Taqqu.
%Fractional ARIMA with Stable Innovations.
%\textit{Stochastic Processes and their Applications}, 1995.

%\bibitem{Adler98}
%R.~Adler, R.~Feldman, M.~Taqqu.
%\textit{A Practical Guide to Heavy Tails: Statistical Techniques and Applications}.
%Birkhauser, Boston MA, 1998.

%\bibitem{Carlson99}
%J.~Carlson, J.~Doyle. Highly optimized tolerance: A mechanism for power laws in designed systems.
%\textit{Physical Review E}, August 1999.

\bibitem{Ross00}
S.~Ross.
\textit{Introduction to probability and statistics for engineers and scientists}.
Harcourt Academic Press, San Diego CA, 2000.

%\bibitem{Downey01}
%A.~Downey.
%The structural cause of file size distributions.
%\textit{Proceedings of the Ninth International Symposium in Modeling, Analysis and Simulation of Computer and Telecommunication Systems (MASCOTS’01)}, 2001.

\bibitem{Ross02}
S.~Ross.
\textit{Probability models for computer science}.
Harcourt Academic Press, San Diego CA, 2002.

%\bibitem{Leland93}
%W.~Leland, M.~Taqq, W.~Willinger, D.~Wilson.
%On the self-similar nature of Ethernet traffic.
%\textit{Proceedings of ACM SIGCOMM'93}, San Francisco CA, 1993.

%\bibitem{Taqqu97}
%S.~Taqqu, W.~Willinger, R.~Sherman.
%Proof of a fundamental result in self-similar traffic modeling.
%\textit{ACM SIGCOMM Computer Communication Review}, 1997

\bibitem{Willinger98}
W.~Willinger, V.~Paxson.
Where mathematics meets the Internet.
\textit{Notices of the American Mathematical Society}, August 1998.

\bibitem{Wolski98}
R.~Wolski.
Dynamically forecasting network performance using the network weather service.
\textit{Journal of Cluster Computing}, 1998.

%\bibitem{Fischer01}
%M.~Fischer, T.~Fowler.
%Fractals, Heavy-Tails and the Internet.
%\textit{Sigma Technology Summaries, 2 (Summer 2001)}, Mitretek Systems Technical Report, 2001.

\bibitem{Brownlee02}
N.~Brownlee, K.~Claffy.
Understanding Internet traffic streams: Dragonflies and tortoises.
\textit{IEEE Communications Magazine}, October 2002.

%\bibitem{Saroiu02}
%S.~Saroiu, P.~Gummadi, S.~Gribble.
%A Measurement Study of Peer-to-Peer File Sharing Systems.
%Technical Report UW-CSE-01-06-02, Department of Computer Science \& Engineering, University of Washington, 2002.

%\bibitem{Willinger02}
%W.~Willinger, R.~Govindan, S.~Jamin, V.~Paxson, S.~Shenker.
%Scaling phenomena in the Internet: Critically examining criticality.
%\textit{Proceedings of the National Academy of Sciences of the United States of America}, February 2002.

\bibitem{Zhang02}
Y.~Zhang, L.~Breslau, V.~Paxson, S.~Shenker.
On the Characteristics and Origins of Internet Flow Rates.
\textit{Proceedings of the 2002 conference on Applications, technologies, architectures, and protocols for computer communications}, 2002.

\bibitem{Estan03}
C.~Estan, S.~Savage, G.~Varghese.
Automatically Inferring Patterns of Resource Consumption in Network Traffic.
\textit{Proceedings of SIGCOMM}, Karlsruhe, Germany, 2003.

%\bibitem{Brevik04}
%J.~Brevik, D.~Nurmi, R.~Wolski.
%Automatic methods for predicting machine availability in desktop grid and peer-to-peer systems.
%\textit{Proceedings of Fourth International Scientific Workshop on Global and Peer-to-Peer Computing}, Chicago IL, 2004.

%\bibitem{Karagiannis04}
%T.~Karagiannis, M.~Molle, M.~Faloustos, A.~Broido.
%A nonstationary poisson view of Internet traffic.
%\textit{Proceedings of IEEE INFOCOM 2004}, March 2004.

%\bibitem{Uhlig04}
%S.~Uhlig.
%Non-stationarity and high-order scaling in TCP flow arrivals: a methodological analysis.
%\textit{ACM SIGCOMM Computer Communications Review}, April 2004.

%\bibitem{Sen04}
%S.~Sen, J.~Wang.
%Analyzing Peer-To-Peer Traffic Across Large Networks.
%\textit{IEEE/ACM Transactions on Networking}, April 2004.

%\bibitem{Wright04}
%C.~Wright, F.~Monrose, G.~Masson.
%HMM Profiles for Network Traffic Classification (Extended Abstract).
%\textit{Proceedings of VizSEC/DMSEC’04}, Washington DC, October 2004.

%\bibitem{Yin05}
%H.~Yin, C.~Lin, B.~Sebastien, B.~Li, G.~Min.
%Network traffic prediction based on a new time series model.
%\textit{International Journal of Communication Systems}, February 2005.

%\bibitem{Karagiannis05}
%T.~Karagiannis, K.~Papagiannaki, M.~Faloutsos.
%BLINC: Multilevel Traffic Classification in the Dark.
%\textit{Proceedings of ACM SIGCOMM}, August 2005.

%\bibitem{Brownlee05}
%N.~Brownlee.
%Some Observations of Internet Stream Lifetimes.
%\textit{Passive and Active Measurement Workshop}, 2005

\bibitem{Liu98}
T.~Liu, P.~Bahl, I.~Chlamtac.
Mobility modeling, location tracking, and trajectory prediction in wireless ATM networks.
\textit{IEEE Journal on Selected Areas in Communications}, 1998.

\bibitem{Tang99}
D.~Tang, M.~Baker. Analysis of a Metropolitan-Area Wireless Network.
\textit{Proceedings of Mobicom 1999}, Seattle WA, Aug 1999.

\bibitem{Tang00}
D.~Tang, M.~Baker. Analysis of a local-area wireless Network. \textit{Proceedings of Mobicom 2000}, Boston MA, 2000.

\bibitem{Kotz02}
D.~Kotz, K.~Essien.
Analysis of a campus-wide wireless network.
\textit{Proceedings of ACM MobiCom 2002}, September 2002.

\bibitem{Balachandran02}
A.~Balachandran, G.~Voelker, P.~Bahl, V.~Rangan.
Characterizing User Behavior and Network Performance in a Public Wireless LAN.
\textit{Proceedings of ACM SIGMETRICS'02}, Marina Del Ray CA, June 2002.

\bibitem{Camp02}
T.~Camp, J.~Boleng, V.~Davies.
A survey of mobility models for ad hoc network research.
\textit{Wireless Communications and Mobile Computing}, September 2002.

\bibitem{Yoon03:speed-decay}
J.~Yoon, M.~Liu, B.~Noble.
Random Waypoint Considered Harmful.
\textit{Proceedings of INFOCOM 2003}, San Francisco, April 2003.

\bibitem{Balazinska03}
M.~Balazinska, P.~Castro.
Characterizing mobility and network usage in a corporate wireless local-area network.
\textit{Proceedings of ACM MobiSys 2003}, May 2003.

\bibitem{Yoon03:sound-models}
J.~Yoon, M.~Liu, B.~Noble.
Sound Mobility Models.
\textit{Proceedings of ACM MobiCom'03}, San Diego CA, September 2003.

\bibitem{Jardosh03}
A.~Jardosh, E.~Belding-Royer, K.~Almeroth, S.~Suri.
Towards Realistic Mobility Models For Mobile Ad hoc Networks.
\textit{Proceedings of ACM MobiCom'03}, San Diego CA, September 2003.

\bibitem{Chinchilla04}
F.~Chinchilla, M.~Lindsey, M.~Papadopouli.
Analysis of wireless information locality and association patterns in a campus.
\textit{Proceedings of IEEE INFOCOM 2004}, March 2004.

\bibitem{Schwab04}
D.~Schwab, R.~Bunt.
Characterizing the use of a campus wireless network.
\textit{Proceedings of IEEE INFOCOM 2004}, March 2004.

\bibitem{Zheng04}
Q.~Zheng, X.~Hong, S.~Ray.
Recent Advances in Mobility Modeling for Mobile Ad Hoc Network Research.
\textit{Proceedings of ACMSE’04}, Huntsville AL, April 2004.

\bibitem{Henderson04}
T.~Henderson, D.~Kotz, I.~Abyzov.
The changing usage of a mature campus-wide wireless network.
\textit{Proceedings of ACM MobiCom 2004}, September 2004.

\bibitem{Meng04}
X.~Meng, S.~Wong, Y.~Yuan, S.~Lu.
Characterizing flows in large wireless data networks.
\textit{Proceedings of ACM MobiCom 2004}, September 2004.

\bibitem{Musolesi04}
M.~Musolesi, S.~Hailes, C.~Mascolo.
An Ad Hoc Mobility Model Founded on Social Network Theory.
\textit{Proceedings of ACM MSWiM’04}, Venezia, Italy, October 2004.

\bibitem{Tuduce05}
C.~Tuduce, T.~Gross.
A Mobility Model Based on WLAN Traces and its Validation.
\textit{Proceedings of IEEE INFOCOM}, March 2005.

\bibitem{Jardosh05}
A.~Jardosh, E.~Belding-Royer, K.~Almeroth, S.~Suri.
Real-World Environment Models for Mobile Network Evaluation.
\textit{IEEE Journal on Selected Areas in Communications}, March 2005.

\bibitem{Papadopouli05:duration-association}
M.~Papadopouli, H.~Shen, M.~Spanakis.
Characterizing the duration and association patterns of wireless access in a campus.
\textit{11th European Wireless Conference}, April 2005.

\end{thebibliography}
